### 2018-04-30 paper/system-model.tex
Updates bibsp again, fixes Sonja's comment in sys model

\name is a distributed system made of users' devices. 
Each device can communicate with any other device that it knows the
address for. All devices belonging to one user
 know which other devices belong to the same user, \ie the \squad.
Thus the devices from an \squad only knows the mapping from devices to users for the devices in 
the \squad it belongs to.

>>>>

\name is a distributed system made of users' devices. 
Each device can communicate with any other device that it knows the
address for (\eg using the Internet). All devices belonging to one user
 know which other devices belong to the same user, \ie the \squad.
Thus the devices from an \squad only knows the mapping from devices to users for the devices in 
the \squad it belongs to.
We also assume that the users can exchange some limited amounts of data 
out-of-band, \ie through some other channel than the network just mentioned (\eg 
using \ac{NFC}).
